---
output:
  md_document:
    variant: markdown_github
---


```{r, eval=FALSE}

rm(list = ls()) # Clean your environment:
gc() # garbage collection - It can be useful to call gc after a large object has been removed, as this may prompt R to return memory to the operating system.
library(tidyverse)
```

# Question 1

```{r, eval=F}
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)


Loc <- "Question1/data/Covid/"
Covid1 <- read_csv(glue::glue("{Loc}owid-covid-data.csv"))
list.files('Question1/code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))

l <- line_bar(alpha = 0.8, size = 1,fig.width=6, fig.height=4)


```
With regards to see differing trends between Africa and other countries 





# Question 2
```{r, eval=F}
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)


Loc1 <- "Question2/data/London/"
London <- read_csv(glue::glue("{Loc1}london_weather.csv"))
UKMonthly_Detailed <- read_csv("~/21641412_Practical/Question2/data/London/UKMonthly_Detailed.csv")
list.files('Question2/code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))


```
er4f
f4ff4



# Question 3
```{r, eval=F}
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)


Loc2 <- "Question3/data/Coldplay_vs_Metallica/"
Spotify_info <- read_csv(glue::glue("{Loc2}Broader_Spotify_Info.csv"))
Coldplay <- read_csv(glue::glue("{Loc2}Coldplay.csv"))
metallica <- read_csv(glue::glue("{Loc2}metallica.csv"))


```


here is the barplot

```{r, warning=FALSE}
library(tidyverse)
Loc2 <- "Question3/data/Coldplay_vs_Metallica/"
metallica <- read_csv(glue::glue("{Loc2}metallica.csv"))
list.files('Question3/code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))
f <- geom_bar1(alpha = 0.7, fig.width=6, fig.height= 20)
```
The following is found 
here



# Question 4
```{r, eval=F}
Loc3 <- "Question4/data/netflix/"
credit<- read_csv(glue::glue("{Loc3}credits.csv"))
titles <- read_csv(glue::glue("{Loc3}titles.csv"))

list.files('Question4/code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))

m <- Movie_vs_series(alpha = 0.7)
m

```

This is why the following 

```{r}
Loc3 <- "Question4/data/netflix/"
credit<- read_csv(glue::glue("{Loc3}credits.csv"))
titles <- read_csv(glue::glue("{Loc3}titles.csv"))
list.files('Question4/code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))

m2 <- table_of_extremes()
m2

```
To extrapolate further on the possible benefit of focusing on shows as oppose to movies is displayed in the table above. Filtering the dataframe into only movies and shows respectively allows one to get the percewntage of movies above a rating of 7 and below a rating of 5 (the same for shows). This illustrates that shows exhibit an imdb rating of higher than 7 almost 50% of the time. Furthermore, there are no show with a rating under 5. Movies are typically more hit and miss.

Future analysis to be done could be to weigh how this obvious pro for Shows relates to costs for producing shows vs movies (given shows are longer one would expect a bigger budget required). This insight could ultimately decide what to put more focus on. 

# Question 5

```{r, eval=F, warning=FALSE}
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)


Loc4 <- "Question5/data/googleplay/"
User_reviews<- read_csv(glue::glue("{Loc4}googleplaystore_user_reviews.csv"))
google_playstore <- read_csv(glue::glue("{Loc4}googleplaystore.csv"))
```

First I made use of Geom_col in order to extract the most profitable apps from different categories

```{r, warning=FALSE}
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)


Loc4 <- "Question5/data/googleplay/"
User_reviews<- read_csv(glue::glue("{Loc4}googleplaystore_user_reviews.csv"))
google_playstore <- read_csv(glue::glue("{Loc4}googleplaystore.csv"))

list.files('Question5/code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))

g <- profitability(alpha = 0.7)

```
Here I made use of the geom_col function to look at the most profitable categories of apps. 


```{r, warning=FALSE}
list.files('Question5/code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))

f <- size_summary(ignore.case = TRUE)

```
Here we looked at the average size, minimum size and maximum size of the apps given for the given categories. They are also rank ordered from highest to lowest average size 








