---
output:
  md_document:
    variant: markdown_github
---


```{r, eval=FALSE}

rm(list = ls()) # Clean your environment:
gc() # garbage collection - It can be useful to call gc after a large object has been removed, as this may prompt R to return memory to the operating system.
library(tidyverse)
```

# Question 1

```{r, echo=FALSE, eval=F}
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)


Loc <- "Question1/data/Covid/"
Covid1 <- read_csv(glue::glue("{Loc}owid-covid-data.csv"))
list.files('Question1/code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))

l <- line_bar(alpha = 0.8, size = 1)
```
With regards to see differing trends between Africa and other countries 





# Question 2
```{r, eval=F}
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)


Loc1 <- "Question2/data/London/"
London <- read_csv(glue::glue("{Loc1}london_weather.csv"))
UKMonthly_Detailed <- read_csv("~/21641412_Practical/Question2/data/London/UKMonthly_Detailed.csv")
list.files('Question2/code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))
```
er4f
f4ff4



# Question 3
```{r, eval=F}
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)


Loc2 <- "Question3/data/Coldplay_vs_Metallica/"
Spotify_info <- read_csv(glue::glue("{Loc2}Broader_Spotify_Info.csv"))
Coldplay <- read_csv(glue::glue("{Loc2}Coldplay.csv"))
metallica <- read_csv(glue::glue("{Loc2}metallica.csv"))

```


here is the barplot

```{r,fig.width=6,fig.height=4}

```
The following is found 
here



# Question 4
```{r, eval=F}
Loc3 <- "Question4/data/netflix/"
credit<- read_csv(glue::glue("{Loc3}credits.csv"))
titles <- read_csv(glue::glue("{Loc3}titles.csv"))
```

This is why the following 



# Question 5

```{r, eval=F, warning=FALSE}
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)


Loc4 <- "Question5/data/googleplay/"
User_reviews<- read_csv(glue::glue("{Loc4}googleplaystore_user_reviews.csv"))
google_playstore <- read_csv(glue::glue("{Loc4}googleplaystore.csv"))
```

First I made use of Geom_col in order to extract the most profitable apps from different categories

```{r, warning=FALSE}
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)


Loc4 <- "Question5/data/googleplay/"
User_reviews<- read_csv(glue::glue("{Loc4}googleplaystore_user_reviews.csv"))
google_playstore <- read_csv(glue::glue("{Loc4}googleplaystore.csv"))

list.files('Question5/code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))

g <- profitability(alpha = 0.7)

```
Here I made use of the geom_col function to look at the most profitable categories of apps. 


```{r, warning=FALSE}
list.files('Question5/code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))

f <- size_summary(ignore.case = TRUE)

```
Here we looked at the average size, minimum size and maximum size of the apps given for the given categories. They are also rank ordered from highest to lowest average size 








