---
output:
  md_document:
    variant: markdown_github
---


```{r, eval=FALSE, echo=FALSE}

rm(list = ls()) # Clean your environment:
gc() # garbage collection - It can be useful to call gc after a large object has been removed, as this may prompt R to return memory to the operating system.
library(tidyverse)
```

# Question 1

```{r, warning=FALSE}
library(tidyverse)


Loc <- "Question1/data/Covid/"
suppressMessages({Covid1 <- read_csv(glue::glue("{Loc}owid-covid-data.csv"))})
list.files('Question1/code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))

l <- line_bar(alpha = 0.8, size = 1,fig.width=6, fig.height=4)


```

Here the idea was to see whether or not there was a difference between the ratio of deaths to cases (wrt Covid) in different regions of the world (especially Africa). Not much is revealed through the data except for the fact that Africa seemed to remain at constant level which differs from the other regions. 



```{r, warning=FALSE}
library(tidyverse)

Loc <- "Question1/data/Covid/"
suppressMessages({Covid1 <- read_csv(glue::glue("{Loc}owid-covid-data.csv"))})
list.files('Question1/code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))

l1 <- top2_bottom2()

```
Above through some wrangling I wanted to understand how something like poverty levels (vastly different from country to country) could have different effect on the deaths from covid. 
Now we now that Jordan and Kazakhstan on average have the least amount of poverty, where as the Democratic republic of Congo and Madagascar exhibit the highest level of poverty. Given this we can see how poverty relates to the number of covid deaths. Perhaps surprisingly Jordan are one of the countr

```{r, warning=FALSE}
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)

Loc <- "Question1/data/Covid/"
suppressMessages({Covid1 <- read_csv(glue::glue("{Loc}owid-covid-data.csv"))})
list.files('Question1/code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))

l2 <- Poverty_rates(alpha = 0.7)
l2

```
The following was done using the results from the above table and simply graphing the total deaths (per million) using a geom_line function for the respective countries. The results suggest that countries with higher average poverty report far lower total deaths as compared to those with lower levels of poverty. These results seems suspicious on surface level. There is thus a need for futher investigation, perhaps less reporting are done in 'poorer' countries or the reporting done is faulty. Another approach would be an econometric analysis of the effect of poverty on covid deaths which would shed light into whether these relationships are subject to significant covariates that explains the reason for the graph above. 

# Question 2
```{r, warning=FALSE}

library(tidyverse)


Loc1 <- "Question2/data/London/"
suppressMessages({London <- read_csv(glue::glue("{Loc1}london_weather.csv"))})
suppressMessages({UKMonthly_Detailed <- read_csv("~/21641412_Practical/Question2/data/London/UKMonthly_Detailed.csv")})
list.files('Question2/code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))

s1 <- London_is_cold(alpha = 0.7)
s1

```

the idea here was to point out in a visually pleasing manner how the mean temperatures from London varies through the months and the years, however some technical difficulties was encountered.....

the graph that follows does a similar job in a less appealing way. 


```{r}
library(tidyverse)


Loc1 <- "Question2/data/London/"
suppressMessages({London <- read_csv(glue::glue("{Loc1}london_weather.csv"))})
suppressMessages({UKMonthly_Detailed <- read_csv("~/21641412_Practical/Question2/data/London/UKMonthly_Detailed.csv")})
list.files('Question2/code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))

s2 <- London_weather(alpha = 0.7)
s2

```
The mean temperatures in London over the years has not changed that much and considering the fact that its mean temp remains around 10 suggest in and of itself that no thinking person (from SA) will particularly enjoy the weather. 





# Question 3
```{r, warning=FALSE}
library(tidyverse)


Loc2 <- "Question3/data/Coldplay_vs_Metallica/"
suppressMessages({Spotify_info <- read_csv(glue::glue("{Loc2}Broader_Spotify_Info.csv"))})
suppressMessages({Coldplay <- read_csv(glue::glue("{Loc2}Coldplay.csv"))})
suppressMessages({metallica <- read_csv(glue::glue("{Loc2}metallica.csv"))})


```


here is the barplot

```{r, warning=FALSE}
library(tidyverse)
Loc2 <- "Question3/data/Coldplay_vs_Metallica/"
suppressMessages({metallica <- read_csv(glue::glue("{Loc2}metallica.csv"))})
list.files('Question3/code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))
f <- geom_bar1(alpha = 0.7, fig.width=6, fig.height= 20)
```
The following boxplot was created to see the popularity of Metallica's albums. First, it was required to filter out those albums that are reproduced and then those that were live albums. The remaining albums produces the boxplot from above. 



# Question 4
```{r, warning=FALSE}
Loc3 <- "Question4/data/netflix/"
suppressMessages({credit<- read_csv(glue::glue("{Loc3}credits.csv"))})
suppressMessages({titles <- read_csv(glue::glue("{Loc3}titles.csv"))})

list.files('Question4/code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))

m <- Movie_vs_series(alpha = 0.7,fig.width=6, fig.height=4)
m

```
To create the graphic above I simply summarised the data as it relates to the two variables at hand (movies and Series/Shows). Then the average Imdb rating was used to see whether its smarter to invest into movies or series (if quality is what you are after). The results suggest that series has a better average rating compared to movies. 

```{r}
Loc3 <- "Question4/data/netflix/"
suppressMessages({credit<- read_csv(glue::glue("{Loc3}credits.csv"))})
suppressMessages({titles <- read_csv(glue::glue("{Loc3}titles.csv"))})
list.files('Question4/code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))

m2 <- table_of_extremes()
m2

```
To extrapolate further on the possible benefit of focusing on shows as oppose to movies is displayed in the table above. Filtering the dataframe into only movies and shows respectively allows one to get the percewntage of movies above a rating of 7 and below a rating of 5 (the same for shows). This illustrates that shows exhibit an imdb rating of higher than 7 almost 50% of the time. Furthermore, there are no show with a rating under 5. Movies are typically more hit and miss.

Future analysis to be done could be to weigh how this obvious pro for Shows relates to costs for producing shows vs movies (given shows are longer one would expect a bigger budget required). This insight could ultimately decide what to put more focus on. 

# Question 5

```{r, warning=FALSE}
library(tidyverse)


Loc4 <- "Question5/data/googleplay/"
suppressMessages({User_reviews<- read_csv(glue::glue("{Loc4}googleplaystore_user_reviews.csv"))})
suppressMessages({google_playstore <- read_csv(glue::glue("{Loc4}googleplaystore.csv"))})

list.files('Question5/code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))

g <- profitability(alpha = 0.7)

```
Here I made use of the geom_col function to look at the most profitable categories of apps. In this case (looking at profitability) I only looked at apps that were paid for (not free ones). This was done through filtering the data for only the paid apps. Then looking at each category to see whether any stands out. From the figure its clear that Family, Finance, Lifestyle and medical are the categories of apps that garners the most profits. These tend to be the apps that are typically not free, but they are also typically the apps that consumers would pay for.


```{r, warning=FALSE}
list.files('Question5/code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))

f <- size_summary(ignore.case = TRUE)

```
Here we looked at the average size, minimum size and maximum size of the apps given for the given categories. They are also rank ordered from highest to lowest average size. This table was created through focussing on the categories and the size variables. Through some wrangling and summarising this is the end result. As expected the size of gaming, family, Travel & local and Sports are the biggest. 








