---
output:
  md_document:
    variant: markdown_github
---


```{r, eval=FALSE, echo=FALSE}

rm(list = ls()) # Clean your environment:
gc() # garbage collection - It can be useful to call gc after a large object has been removed, as this may prompt R to return memory to the operating system.
library(tidyverse)
```

# Question 1

```{r, warning=FALSE}
library(tidyverse)


Loc <- "Question1/data/Covid/"
suppressMessages({Covid1 <- read_csv(glue::glue("{Loc}owid-covid-data.csv"))})
list.files('Question1/code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))

l <- line_bar(alpha = 0.8, size = 1,fig.width=6, fig.height=4)


```


With regards to see differing trends between Africa and other countries 


```{r, warning=FALSE}
library(tidyverse)

Loc <- "Question1/data/Covid/"
suppressMessages({Covid1 <- read_csv(glue::glue("{Loc}owid-covid-data.csv"))})
list.files('Question1/code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))

l1 <- top2_bottom2()

```

Now we now that Jordan and Kazakhstan on average have the least amount of poverty, where as the Democratic republic of Congo and Madagascar exhibit the highest level of poverty. Given this we can see how poverty relates to the number of covid deaths. Perhaps surprisingly Jordan are one of the countr

```{r, warning=FALSE}
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)

Loc <- "Question1/data/Covid/"
suppressMessages({Covid1 <- read_csv(glue::glue("{Loc}owid-covid-data.csv"))})
list.files('Question1/code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))

l2 <- Poverty_rates(alpha = 0.7)
l2

```
The following was done using the results from the above table and simply graphing the total deaths (per million) using a geom_line function for the respective countries. The results suggest that countries with higher average poverty report far lower total deaths as compared to those with lower levels of poverty. These results seems suspicious on surface level. There is thus a need for futher investigation, perhaps less reporting are done in 'poorer' countries or the reporting done is faulty. Another approach would be an econometric analysis of the effect of poverty on covid deaths which would shed light into whether these relationships are subject to significant covariates that explains the reason for the graph above. 

# Question 2
```{r, warning=FALSE}

library(tidyverse)


Loc1 <- "Question2/data/London/"
suppressMessages({London <- read_csv(glue::glue("{Loc1}london_weather.csv"))})
suppressMessages({UKMonthly_Detailed <- read_csv("~/21641412_Practical/Question2/data/London/UKMonthly_Detailed.csv")})
list.files('Question2/code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))

s1 <- London_is_cold(alpha = 0.7)
s1

```

the idea here was to point out in a visually pleasing manner 


```{r}
library(tidyverse)


Loc1 <- "Question2/data/London/"
suppressMessages({London <- read_csv(glue::glue("{Loc1}london_weather.csv"))})
suppressMessages({UKMonthly_Detailed <- read_csv("~/21641412_Practical/Question2/data/London/UKMonthly_Detailed.csv")})
list.files('Question2/code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))

s2 <- London_weather(alpha = 0.7)
s2

```






# Question 3
```{r, warning=FALSE}
library(tidyverse)


Loc2 <- "Question3/data/Coldplay_vs_Metallica/"
suppressMessages({Spotify_info <- read_csv(glue::glue("{Loc2}Broader_Spotify_Info.csv"))})
suppressMessages({Coldplay <- read_csv(glue::glue("{Loc2}Coldplay.csv"))})
suppressMessages({metallica <- read_csv(glue::glue("{Loc2}metallica.csv"))})


```


here is the barplot

```{r, warning=FALSE}
library(tidyverse)
Loc2 <- "Question3/data/Coldplay_vs_Metallica/"
suppressMessages({metallica <- read_csv(glue::glue("{Loc2}metallica.csv"))})
list.files('Question3/code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))
f <- geom_bar1(alpha = 0.7, fig.width=6, fig.height= 20)
```
The following is found 
here



# Question 4
```{r, warning=FALSE}
Loc3 <- "Question4/data/netflix/"
suppressMessages({credit<- read_csv(glue::glue("{Loc3}credits.csv"))})
suppressMessages({titles <- read_csv(glue::glue("{Loc3}titles.csv"))})

list.files('Question4/code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))

m <- Movie_vs_series(alpha = 0.7,fig.width=6, fig.height=4)
m

```

This is why the following 

```{r}
Loc3 <- "Question4/data/netflix/"
suppressMessages({credit<- read_csv(glue::glue("{Loc3}credits.csv"))})
suppressMessages({titles <- read_csv(glue::glue("{Loc3}titles.csv"))})
list.files('Question4/code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))

m2 <- table_of_extremes()
m2

```
To extrapolate further on the possible benefit of focusing on shows as oppose to movies is displayed in the table above. Filtering the dataframe into only movies and shows respectively allows one to get the percewntage of movies above a rating of 7 and below a rating of 5 (the same for shows). This illustrates that shows exhibit an imdb rating of higher than 7 almost 50% of the time. Furthermore, there are no show with a rating under 5. Movies are typically more hit and miss.

Future analysis to be done could be to weigh how this obvious pro for Shows relates to costs for producing shows vs movies (given shows are longer one would expect a bigger budget required). This insight could ultimately decide what to put more focus on. 

# Question 5

```{r, eval=F, warning=FALSE}
library(tidyverse)


Loc4 <- "Question5/data/googleplay/"
suppressMessages({User_reviews<- read_csv(glue::glue("{Loc4}googleplaystore_user_reviews.csv"))})
suppressMessages({google_playstore <- read_csv(glue::glue("{Loc4}googleplaystore.csv"))})
```

First I made use of Geom_col in order to extract the most profitable apps from different categories

```{r, warning=FALSE}
library(tidyverse)


Loc4 <- "Question5/data/googleplay/"
suppressMessages({User_reviews<- read_csv(glue::glue("{Loc4}googleplaystore_user_reviews.csv"))})
suppressMessages({google_playstore <- read_csv(glue::glue("{Loc4}googleplaystore.csv"))})

list.files('Question5/code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))

g <- profitability(alpha = 0.7)

```
Here I made use of the geom_col function to look at the most profitable categories of apps. 


```{r, warning=FALSE}
list.files('Question5/code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))

f <- size_summary(ignore.case = TRUE)

```
Here we looked at the average size, minimum size and maximum size of the apps given for the given categories. They are also rank ordered from highest to lowest average size 








